The globular cluster system of the Auriga simulations

### 2019-08-18 AurigaGCS.tex
Updated Figure 4 and 6 for #1
Updated Figure 5 and 7 for #1

% Abstract of the paper
\begin{abstract}
We investigate whether the galaxy formation model used for the Auriga simulations
can produce a realistic globular cluster (GC) population at redshift zero. We
compare properties of the simulated star particles in the Auriga haloes with
catalogues of observations of the Milky Way (MW) and Andromeda (M31) globular
cluster populations available in the literature. We find that the Auriga 
simulations do produce sufficient mass at radii and metallicities that are 
typical for the MW globular cluster system (GCS), although we observe a varying 
mass-excess for different galactocentric radius-metallicity 
($R_{\text{gal}}$-[Fe/H]) bins of simulated GC candidates
relative to the observed mass in the MW and M31 GC systems. This implies different 
values for the combined product of the bound cluster formation efficiency and 
the globular cluster disruption rate. Furthermore we test whether any of the 
Auriga galaxies has a metallicity and radial distribution that is consistent with 
the MW or M31 GCS. For any one of the Auriga haloes we reject the null hypothesis
that the observed and simulated metallicities of GCs (GC candidates) are drawn
from the same distribution at $\geq98.32$~\% confidence level, for the GCS of 
the Milky Way as well as that of the Andromeda galaxy. The same holds true for 
the distribution of $R_{\text{gal}}$ . Overall, the Auriga simulations produce 
old star particles with higher metallicities than the MW and M31 GCS and at 
larger radii. The formation efficiency would have to linearly decrease with 
increasing metallicity for the Auriga GC candidates to be consistent with the 
MW GCS, if cluster disruption is equally efficient regardless of metallicity.
In addition, the number of GCs relative to field stars would have to be smaller
for higher metallicity star particles at large radii than for those with lower 
metallicity at smaller radii, assuming GC disruption is more efficient in the
inner regions of the Galaxy.

@@

\begin{figure}
    \includegraphics[width=\columnwidth]{{FeH_mu_sigma-trim}.png}
    \caption{
        First vs second central moment of the Auriga L4 metallicity distributions.
        Each cross (for a given colour) represents one simulation. The green (blue)
        [red] crosses show the values calculated using the old (old {\it in~situ})
        [old accreted] star particles. Green triangles indicate that all stars
        were used. The purple (magenta) cross denotes our calculation using all
        MW (M31) observations (which would be appropriate for a unimodal
        distribution). The black solid (open) dots indicate the literature values
        of a bimodal Gaussian fit to the data \citep[values from][p. 38]{1998gcs..book.....A},
        showing the metal-rich (metal-poor) component of the MW.
        \label{fig:FeH_mu_sigma}
    }
\end{figure}

@@

We show the ratio of the  simulated to the observed profiles in the middle (bottom) 
panel. This mass excess can be thought of the `mass budget' that the Auriga GC 
candidates can `afford to lose' due to a combination of smaller than unity bound
cluster formation efficiencies combined with a Hubble time of dynamical evolution,
while still producing sufficient mass at the right metallicities. In particular,
the cluster formation efficiency would have to decrease with decreasing 
metallicity for Auriga GC candidates to produce a population of GC candidates 
that is consistent with the MW. For the GC candidates in M31 we find a constant 
mass excess up to $-0.9$, above which the simulations produce a higher mass excess 
with increasing metallicity. If dynamical evolution is not expected to more 
efficiently disrupt GCs of higher metallicity, then we would find that the 
efficiency to form bound star clusters would have to decrease with increasing 
metallicity.

@@

\begin{figure}
    \includegraphics[width=\columnwidth]{{logMRgc_withRatios-trim}.png}
    \caption{
        Mass-weighted radial distribution of star particles in the Auriga
        simulations. We show the median value of all Auriga haloes for all
        stars (green dotted) and globular cluster candidates (i.e. stars with
        age $>$~10~Gyr; green solid). The latter sub set is further split up
        between stars that formed {\it in~situ} (blue solid), and those that 
        were accreted (red solid). Shaded regions indicate the $1\sigma$ 
        interval. The MW (M31) GCS is shown in purple (magenta). The middle 
        (bottom) panel shows the ratio of the simulated mass to the mass in the 
        MW (M31) GCS.
        \label{fig:Rgc}
    }
\end{figure}
Figure~\ref{fig:Rgc} shows the mass-weighted radial distribution of the
Auriga L4 haloes. We notice a subtle peak around $10$~kpc for all star
particles that is not present for the GC candidates, indicating that the
stellar disc is no longer present when applying the latter selection criterion.
Furthermore, we find that the dominant contribution to the total mass in GC
candidates changes from those formed {\it in~situ} to the accreted population around
$10$~kpc. Again we show the mass excess of the simulations compared to the Milky
Way and Andromeda GCS. We find a decreasing mass excess with increasing radius
in the range $0.2$ to ${\sim}5$ kpc, followed by an increase attributed
to the accreted subpopulation. For the Milky Way we notice that significantly
fewer GCs are found beyond $40$~kpc than for M31, and that accreted GC candidates
contribute mostly to the Auriga GCS at these radii. We further investigate a 
breakdown of the total mass in Auriga GC candidates into bins of both metallicity 
and radius in the following section.

@@

We investigate whether the Auriga simulations still produce sufficient mass when
the GC candidates are two-dimensionally binned in [Fe/H] and $R_\text{gal}$. First
we sum the total simulated mass in each bin (for an individual Auriga simulation),
then we calculate the median over all thirty Auriga L4 haloes (in each bin, see
Figure~\ref{fig:Au-FeHRgc} which can be compared to
Figure~\ref{fig:observations_FeHRgc}). Finally, we divide these value by the total
mass in the MW (M31) GCS to obtain the median mass excess produced by the star
formation model implemented in the Auriga simulations. See the top (bottom) panel
of Figure~\ref{fig:Au-FeHRgc-ratio} for mass excess with respect to the MW (M31) GCS.

@@

We notice in Figure~\ref{fig:Au-FeHRgc} that the Auriga simulations, on average,
produce fewer GCs in the lowest metallicity bins ($-2.5$ to $-1.5$) than at higher 
metallicities in the three innermost radial bins. In addition, Auriga produces 
fewer high-metallicity GCs at large radii, similar to the MW and M31 GC systems. 
However, the three bins in the upper right corner are populated in the Auriga
simulations, in contrast to the observations. The top panel of 
Figure~\ref{fig:Au-FeHRgc-ratio} shows that the mass excess for Auriga GCs within
the Solar radius decreases with decreasing metallicity. This means that either
the formation efficiency should increase with decreasing metallicity, or that 
the lowest-metallicity GCs in the Auriga simulations are less strongly affected
by disruptive processes, if the star formation histories in the Auriga simulations
are to give rise to a GC system that can be similar to the GCS that is observed
in the Milky Way. Moreover, either a lower formation efficiency is required at
large radii, or stronger disruption. Disruption of star clusters is expected to
be more efficient at smaller radii due to higher tidal forces in the innermost
region for GCs on orbits that pass through the disk, or with pericenters close 
to the bar or bulge. Compared to Andromeda, the mass excess (bottom panel of 
Figure~\ref{fig:Au-FeHRgc-ratio}) shows a less clear trend than for the Milky Way,
which suggests that both galaxies have diverse GC formation histories.
Most bins show mass surplus factors of few tens, meaning that high formation 
efficiencies would be required in addition to little disruption for the Auriga 
simulations to yield a GC system consistent with that of the Andromeda galaxy.

\begin{figure}
    \includegraphics[width=0.49\textwidth]
        {{Au4-median_RgcFeH_HistogramMassWeighted_MW_iold-trim}.png}
    \includegraphics[width=0.49\textwidth]
        {{Au4-median_RgcFeH_HistogramMassWeighted_M31_iold-trim}.png}
    \caption{
        The top (bottom) panel shows the logarithm of the ratio of simulated mass
        to mass in the MW (M31) GCS, i.e. the logarithm of the mass excess. The
        number in each bin shows the color-coded value that is plotted, and the
        (median) star particle count is given in parenthesis. Note that the three 
        bins in the upper right corner are left blank because the observations
        have zero mass there.
        \label{fig:Au-FeHRgc-ratio}
    }
\end{figure}

>>>>

% Abstract of the paper
\begin{abstract}
We investigate whether the galaxy formation model used for the Auriga simulations
can produce a realistic globular cluster (GC) population at redshift zero. We
compare properties of the simulated star particles in the Auriga haloes with
catalogues of observations of the Milky Way (MW) and Andromeda (M31) globular
cluster populations available in the literature. We find that the Auriga 
simulations do produce sufficient mass at radii and metallicities that are 
typical for the MW globular cluster system (GCS), although we observe a varying 
mass-ratio for different galactocentric radius-metallicity 
($R_{\text{gal}}$-[Fe/H]) bins of simulated GC candidates
relative to the observed mass in the MW and M31 GC systems. This implies different 
values for the combined product of the bound cluster formation efficiency and 
the globular cluster disruption rate. Furthermore we test whether any of the 
Auriga galaxies has a metallicity and radial distribution that is consistent with 
the MW or M31 GCS. For any one of the Auriga haloes we reject the null hypothesis
that the observed and simulated metallicities of GCs (GC candidates) are drawn
from the same distribution at $\geq98.32$~\% confidence level, for the GCS of 
the Milky Way as well as that of the Andromeda galaxy. The same holds true for 
the distribution of $R_{\text{gal}}$ . Overall, the Auriga simulations produce 
old star particles with higher metallicities than the MW and M31 GCS and at 
larger radii. The formation efficiency would have to linearly decrease with 
increasing metallicity for the Auriga GC candidates to be consistent with the 
MW GCS, if cluster disruption is equally efficient regardless of metallicity.
In addition, the number of GCs relative to field stars would have to be smaller
for higher metallicity star particles at large radii than for those with lower 
metallicity at smaller radii, assuming GC disruption is more efficient in the
inner regions of the Galaxy.

@@

\begin{figure}
    \includegraphics[width=\columnwidth]{{FeH_mu_sigma-trim}.png}
    \caption{
        First vs. second central moment of the Auriga L4 metallicity distributions.
        Each cross (for a given colour) represents one simulation. The green (blue)
        [red] crosses show the values calculated using the old (old {\it in~situ})
        [old accreted] star particles. Green triangles indicate that all stars
        were used. The purple (magenta) cross denotes our calculation using all
        MW (M31) observations (which would be appropriate for a unimodal
        distribution). The black solid (open) dots indicate the literature values
        of a bimodal Gaussian fit to the data \citep[values from][p. 38]{1998gcs..book.....A},
        showing the metal-rich (metal-poor) component of the MW.
        \label{fig:FeH_mu_sigma}
    }
\end{figure}

@@

We show the ratio of the  simulated to the observed profiles in the middle (bottom) 
panel. This mass excess can be thought of the `mass budget' that the Auriga GC 
candidates can `afford to lose' due to a combination of smaller than unity bound
cluster formation efficiencies combined with a Hubble time of dynamical evolution,
while still producing sufficient mass at the right metallicities. In particular,
the cluster formation efficiency would have to decrease with decreasing 
metallicity for Auriga GC candidates to produce a population of GC candidates 
that is consistent with the MW. For the GC candidates in M31 we find a constant 
mass ratio up to $-0.9$, above which the simulations produce a higher mass ratio 
with increasing metallicity. If dynamical evolution is not expected to more 
efficiently disrupt GCs of higher metallicity, then we would find that the 
efficiency to form bound star clusters would have to decrease with increasing 
metallicity.

@@

\begin{figure}
    \includegraphics[width=\columnwidth]{{logMRgc_withRatios-trim}.png}
    \caption{
        Mass-weighted radial distribution of star particles in the Auriga
        simulations. We show the median value of all Auriga haloes for all
        stars (green dotted) and globular cluster candidates (i.e. stars with
        age $>$~10~Gyr; green solid). The latter sub set is further split up
        between stars that formed {\it in~situ} (blue solid), and those that 
        were accreted (red solid). Shaded regions indicate the $1\sigma$ 
        interval. The MW (M31) GCS is shown in purple (magenta). The middle 
        (bottom) panel shows the ratio of the simulated mass to the mass in the 
        MW (M31) GCS.
        \label{fig:Rgc}
    }
\end{figure}
Figure~\ref{fig:Rgc} shows the mass-weighted radial distribution of the
Auriga L4 haloes. We notice a subtle peak around $10$~kpc for all star
particles that is not present for the GC candidates, indicating that the
stellar disc is no longer present when applying the latter selection criterion.
Furthermore, we find that the dominant contribution to the total mass in GC
candidates changes from those formed {\it in~situ} to the accreted population around
$10$~kpc. Again we show the mass ratio of the simulations compared to the Milky
Way and Andromeda GCS. We find a decreasing mass ratio with increasing radius
in the range $0.2$ to ${\sim}5$ kpc, followed by an increase attributed
to the accreted subpopulation. For the Milky Way we notice that significantly
fewer GCs are found beyond $40$~kpc than for M31, and that accreted GC candidates
contribute mostly to the Auriga GCS at these radii. We further investigate a 
breakdown of the total mass in Auriga GC candidates into bins of both metallicity 
and radius in the following section.

@@

We investigate whether the Auriga simulations still produce sufficient mass when
the GC candidates are two-dimensionally binned in [Fe/H] and $R_\text{gal}$. First
we sum the total simulated mass in each bin (for an individual Auriga simulation),
then we calculate the median over all thirty Auriga L4 haloes (in each bin, see
Figure~\ref{fig:Au-FeHRgc} which can be compared to
Figure~\ref{fig:observations_FeHRgc}). Finally, we divide these value by the total
mass in the MW (M31) GCS to obtain the median mass ratio produced by the star
formation model implemented in the Auriga simulations. See the top (bottom) panel
of Figure~\ref{fig:Au-FeHRgc-ratio} for mass ratio with respect to the MW (M31) GCS.

@@

We notice in Figure~\ref{fig:Au-FeHRgc} that the Auriga simulations, on average,
produce fewer GCs in the lowest metallicity bins ($-2.5$ to $-1.5$) than at higher 
metallicities in the three innermost radial bins. In addition, Auriga produces 
fewer high-metallicity GCs at large radii, similar to the MW and M31 GC systems. 
However, the three bins in the upper right corner are populated in the Auriga
simulations, in contrast to the observations. The top panel of 
Figure~\ref{fig:Au-FeHRgc-ratio} shows that the mass ratio for Auriga GCs within
the Solar radius decreases with decreasing metallicity. This means that either
the formation efficiency should increase with decreasing metallicity, or that 
the lowest-metallicity GCs in the Auriga simulations are less strongly affected
by disruptive processes, if the star formation histories in the Auriga simulations
are to give rise to a GC system that can be similar to the GCS that is observed
in the Milky Way. Moreover, either a lower formation efficiency is required at
large radii, or stronger disruption. Disruption of star clusters is expected to
be more efficient at smaller radii due to higher tidal forces in the innermost
region for GCs on orbits that pass through the disk, or with pericenters close 
to the bar or bulge. Compared to Andromeda, the mass ratio (bottom panel of 
Figure~\ref{fig:Au-FeHRgc-ratio}) shows a less clear trend than for the Milky Way,
which suggests that both galaxies have diverse GC formation histories.
Most bins show mass surplus factors of few tens, meaning that high formation 
efficiencies would be required in addition to little disruption for the Auriga 
simulations to yield a GC system consistent with that of the Andromeda galaxy.

\begin{figure}
    \includegraphics[width=0.49\textwidth]
        {{Au4-median_RgcFeH_HistogramMassWeighted_MW_iold-trim}.png}
    \centering \textcolor{lightgray}{\rule[2mm]{\columnwidth}{0.05mm}}
    \includegraphics[width=0.49\textwidth]
        {{Au4-median_RgcFeH_HistogramMassWeighted_M31_iold-trim}.png}
    \caption{
        The top (bottom) panel shows the logarithm of the ratio of simulated mass
        to mass in the MW (M31) GCS, i.e. the logarithm of the mass ratio. The
        number in each bin shows the color-coded value that is plotted, and the
        (median) star particle count is given in parenthesis. Note that the three 
        bins in the upper right corner are left blank because the observations
        have zero mass there.
        \label{fig:Au-FeHRgc-ratio}
    }
\end{figure}
